Weather and fuel as modulators of grassland fire behavior in the northern Great Plains

### 2022-01-25 paper/FigureGenerator.Rmd
begin revisions

`r f_nums('violin_plots')`
```{r data_summary_gg, fig.cap = violin_cap, fig.height=7.5, fig.width=6}
LongData <- 
    read_csv(url('https://raw.githubusercontent.com/devanmcg/SpatialFireBehavior/main/data/AnalysisDataKY.csv')) %>% 
    select(-LAI, -JD, -MaxWindSpeed) %>%
    mutate(ros = ifelse(ros >= 10, NA, ros), 
           tHa = ifelse(tHa >=4, NA, tHa)) %>%
    pivot_longer(cols = AirTemp:tHa, 
                 names_to = 'var', 
                 values_to = 'value') %>%
    mutate(type = case_when(
                    var %in% c('MaxC', 
                               'SoilMaxC', 
                               'ros') ~ 'Fire behavior', 
                    var %in% c('tHa',
                               'FuelMoisture') ~ 'Fuel', 
                    TRUE ~ 'Weather' ), 
           var = recode(var, 
                        AirTemp = 'Air temperature (°C)', 
                        RH = 'Relative humidity (%)', 
                        dpC = 'Dew point (°C)', 
                        FuelMoisture = 'Fuel moisture (%)', 
                        tHa = 'Fuel load (t/ha)',
                        MaxC = 'Canopy temp (°C)', 
                        WindSpeed = 'Wind speed (m/s)', 
                        ros = 'Rate of spread (m/s)', 
                        SoilMaxC = 'Soil surface temp (°C)'), 
           location = recode(location, 
                             H = "Hettinger", 
                             CG = "Central Grasslands"))

>>>>

`r f_nums('violin_plots')`
```{r data_summary_gg, fig.cap = violin_cap, fig.height=7.5, fig.width=6}
LongData <- 
    read_csv(url('https://raw.githubusercontent.com/devanmcg/SpatialFireBehavior/main/data/AnalysisDataKY.csv')) %>% 
    select(-LAI, -JD, -MaxWindSpeed) %>%
    mutate(ros = ifelse(ros >= 10, NA, ros), 
           tHa = ifelse(tHa >=4, NA, tHa)) %>%
    pivot_longer(cols = AirTemp:tHa, 
                 names_to = 'var', 
                 values_to = 'value') %>%
    mutate(type = case_when(
                    var %in% c('MaxC', 
                               'SoilMaxC', 
                               'ros') ~ 'Fire behavior', 
                    var %in% c('tHa',
                               'FuelMoisture') ~ 'Fuel', 
                    TRUE ~ 'Weather' ), 
           var = recode(var, 
                        AirTemp = 'Air temperature (°C)', 
                        RH = 'Relative humidity (%)', 
                        dpC = 'Dew point (°C)', 
                        FuelMoisture = 'Fuel moisture (%)', 
                        tHa = 'Fuel load (t/ha)',
                        MaxC = 'Canopy temp (°C)', 
                        WindSpeed = 'Wind speed (km/h)', 
                        ros = 'Rate of spread (m/s)', 
                        SoilMaxC = 'Soil surface temp (°C)'), 
           location = recode(location, 
                             H = "Hettinger", 
                             CG = "Central Grasslands"))
